Model Samples Processing

### 2020-01-22 stats/model.Rmd
update model processing

plot_global_params

plot_global_params %>%
  group_by(parameter, type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))
```

@@

```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()

>>>>

plot_global_params
```

@@

```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(type~parameter, scales = 'free')+
  theme_few()

### 2020-01-22 stats/model_sample_processing.Rmd
update model processing

model <- bind_rows(
  read_csv("../webppl/output/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
  read_csv("../saves/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
)

@@

global_sigma<- model %>%
  filter(b == "sigma")%>%
  select(-a,-b, -e,-f,-h)%>%
    rename(parameter = c,
         type = d,
         value = g)

saveRDS(global_sigma, "../saves/global_sigma.rds")
```

>>>>

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
)

@@

item_sigma<- model %>%
  filter(b == "sigma",
         c == "global_sem_sigmas")%>%
  select(-a,-b, -e,-f,-h)%>%
    rename(parameter = c,
         type = d,
         value = g)

saveRDS(item_sigma, "../saves/item_sigma.rds")

subject_sigma<- model %>%
  filter(b == "sigma", 
         c != "global_sem_sigmas")%>%
  select(-a,-b, -e,-f,-h, -d)%>%
    rename(parameter = c,
         value = g)

saveRDS(subject_sigma, "../saves/subject_sigma.rds")
```
